Leveraging Diversity to Find Bugs in JavaScript Engines

### 2019-02-21 paper/paper.tex
pass on fuzzing

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:false-positives}Distribution of False (FP)
    and True Positives (TP).}
  \begin{tabular}{ccrr}
    \toprule
    & & \radamsa\ & \quickfuzz\ \\
    \midrule
    \multirow{4}{*}{FP} & Undefined Behavior & 26 & 13 \\ % 26 & 9 
    & Timeout/OME & 28 & 13 \\ % 28 & 13
    & * Invalid Input & 39 & 48 \\ % 39 & 48
    & * Error Message Mismatch & 41 & 12 \\ % 41 & 12
    \midrule
    \multirow{2}{*}{TP} & Duplicate & 34 & 28\\ % 34 & 28
    & Bug & 12 & 6\\
    \bottomrule     
  \end{tabular}
\end{table}

>>>>

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:false-positives}Distribution of False (FP)
    and True Positives (TP).}
  \begin{tabular}{ccrr}
    \toprule
    & & \radamsa\ & \quickfuzz\ \\
    \midrule
    \multirow{4}{*}{FP} & Undefined Behavior & 42 & 16 \\ % 26 & 9 
    & Timeout/OME & 30 & 15 \\ % 28 & 13
    & * Invalid Input & 46 & 55 \\ % 39 & 48
    & * Error Message Mismatch & 41 & 12 \\ % 41 & 12
    \midrule
    \multirow{2}{*}{TP} & Duplicate & 34 & 28\\ % 34 & 28
    & Bug & 12 & 6\\
    \bottomrule     
  \end{tabular}
\end{table}
